A generalization of Plackett-Luce likelihoods to incorporate non-independence of competitors

### 2023-01-06 inst/plackett_luce_monster.Rmd
whitespace

```{r,label=definefunctionf}
f <- function (a,b,M){
return(factorial(3)*factorial(2)*(
(a)/(a+a+a+b+b)*(a+M)/(a+a+b+b+M)*(a+M)/(a+b+b+M)*(b)/(b+b+M)+
(a)/(a+a+a+b+b)*(a+M)/(a+a+b+b+M)*(b)/(a+b+b+M)*(a)/(a+b+M)+
(a)/(a+a+a+b+b)*(a+M)/(a+a+b+b+M)*(b)/(a+b+b+M)*(b+M)/(b+a+M)+
(a)/(a+a+a+b+b)*(b)  /(a+a+b+b+M)*(a)/(a+a+b+M)*(a+M)/(a+b+M)+
(a)/(a+a+a+b+b)*(b)  /(a+a+b+b+M)*(a)/(a+a+b+M)*(b)/(b+a+M)+
(a)/(a+a+a+b+b)*(b)  /(a+a+b+b+M)*(b+M)/(b+a+a+M)*(a)/(a+a+M)+
(b)/(a+a+a+b+b)*(a)  /(a+a+a+b+M)*(a+M)/(a+a+b+M)*(a+M)/(a+b+M)+
(b)/(a+a+a+b+b)*(a)  /(a+a+a+b+M)*(a+M)/(a+a+b+M)*(b)/(a+b+M)+
(b)/(a+a+a+b+b)*(a)  /(a+a+a+b+M)*(b)/(b+a+a)*(a)/(a+a)+
(b)/(a+a+a+b+b)*(b+M)/(a+a+a+b+M)*(a)/(a+a+a)*(a)/(a+a)))
}
```

>>>>

```{r,label=definefunctionf}
f <- function (a,b,M){
return(
  factorial(3)*factorial(2)*(
   a/(a+a+a+b+b)*(a+M)/(a+a+b+b+M)*(a+M)/(a+b+b+M)*(b  )/(b+b+M) +
   a/(a+a+a+b+b)*(a+M)/(a+a+b+b+M)*(b  )/(a+b+b+M)*(a  )/(a+b+M) +
   a/(a+a+a+b+b)*(a+M)/(a+a+b+b+M)*(b  )/(a+b+b+M)*(b+M)/(b+a+M) +
   a/(a+a+a+b+b)*(b  )/(a+a+b+b+M)*(a  )/(a+a+b+M)*(a+M)/(a+b+M) +
   a/(a+a+a+b+b)*(b  )/(a+a+b+b+M)*(a  )/(a+a+b+M)*(b  )/(b+a+M) +
   a/(a+a+a+b+b)*(b  )/(a+a+b+b+M)*(b+M)/(b+a+a+M)*(a  )/(a+a+M) +
   b/(a+a+a+b+b)*(a  )/(a+a+a+b+M)*(a+M)/(a+a+b+M)*(a+M)/(a+b+M) +
   b/(a+a+a+b+b)*(a  )/(a+a+a+b+M)*(a+M)/(a+a+b+M)*(b  )/(a+b+M) +
   b/(a+a+a+b+b)*(a  )/(a+a+a+b+M)*(b  )/(b+a+a  )*(a  )/(a+a  ) +
   b/(a+a+a+b+b)*(b+M)/(a+a+a+b+M)*(a  )/(a+a+a  )*(a  )/(a+a  )
   ) 
   )
}
```
